Automatically Proving Equivalence by Type-Safe Reflection

### 2017-05-19 paper-CICM-17/content/3-hierarchyOfTactics.tex
Some additional changes 4

A novelty of our work is that instead of building a prover for a
specific algebraic structure (like ring), we have built a hierarchy of provers
for many algebraic structures. Moreover, each prover reuses components
of the others so that
the various simplifications are not duplicated at the different
levels: the normalisation function of each structure uses as much as possible
the normalisation function of the structure from which it inherits. For
example, the normalisation on monoids reuses the normalisation on semi-groups
in such a way that it does not have to deal with associativity. In this
case, the datatype reflecting terms in semi-groups has
the same expressive power as that for monoids, so a term of a monoid can easily be transformed into a term of a semi-group. However, 
there is a difficulty with
groups and monoids: normalisation for groups
needs to reuse the normalisation for monoids, meaning that
we will have to encode 
negations somehow, which can't be directly expressed in a monoid. For this
reason, we develop some specific encodings.

>>>>

A novelty of our work is that instead of building a prover for a
specific algebraic structure (like ring), we have built a hierarchy of provers
for many algebraic structures. Moreover, each prover reuses components
of the others so that
the various simplifications are not duplicated at the different
levels: the normalisation function of each structure uses as much as possible
the normalisation function of the structure from which it inherits. For
example, the normalisation on monoids reuses the normalisation on semi-groups
in such a way that it does not have to deal with associativity. In this
case, the datatype reflecting terms in semi-groups has
the same expressive power as that for monoids, so a term valid in a monoid can easily be transformed into a corresponding term of a semi-group. However, 
there is a difficulty with
groups and monoids: normalisation for groups
needs to reuse the normalisation for monoids, meaning that
we will have to encode 
negations somehow, which can't be directly expressed in a monoid. For this
reason, we develop some specific encodings.
